Microbiome and hypertension

### 2018-12-18 rrbiome.Rmd
Packages installed

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r libraries}
library(dplyr)
library(phyloseq)
library(microbiome)
```

```{r data}
pseq <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
```

Pseq has readcount `r readcount(pseq)`.

```{r cars}
print(pseq)
summarize_phyloseq(pseq)
meta <- meta(pseq)
taxonomy <- tax_table(pseq)
otu.absolute <- abundances(pseq)
otu.relative <- abundances(pseq, "compositional")

df <- psmelt(pseq)
head(sample_names(pseq))
sample_sums(pseq)
s <- rownames(subset(meta(pseq), nationality == "AFR" & sex == "Female"))
prune_samples(s, pseq)

sample_variables(pseq)

# Calculate diversity for samples
div <- alpha(pseq, index = "shannon")

# Assign the estimated diversity to sample metadata
sample_data(pseq)$diversity <- div

n <- ntaxa(pseq)
topx <- top_taxa(pseq, n = 10)
ranks <- rank_names(pseq)  # Taxonomic levels
taxa  <- taxa(pseq)        # Taxa names at the analysed level
pseq.bac <- subset_taxa(pseq, Phylum == "Bacteroidetes")
# List of Genera in the Bacteroideted Phylum
taxa <- map_levels(NULL, "Phylum", "Genus", pseq)$Bacteroidetes

# With given taxon names
ex2 <- prune_taxa(taxa, pseq)

# Taxa with positive sum across samples
ex3 <- prune_taxa(taxa_sums(pseq) > 0 , pseq)

head(get_taxa_unique(pseq, "Phylum"))

samplename <- sample_names(pseq)[[1]]

# Pick abundances for a particular taxon
tax.abundances <- abundances(pseq)[, samplename]
```
